---
title: "Build and Test Enviroment"
author: "Craig Parman"
date: "10/5/2016"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```
## Introduction

This document lists the R version and package vesions used in the development of
the CoreAPIV2 package. It is built automatically and reflects the latest
versions used. 

## CoreAPIV2 Package Information

```{r}
packageDescription("CoreAPIV2")
```

## R Environment Information

```{r}
library('knitr')

s<-sessionInfo()
enviro<-as.data.frame(s$R.version)

kable(enviro[,1:5], format = "markdown")
kable(enviro[,6:10], format = "markdown")
kable(enviro[,11:length(enviro)], format = "markdown")
```

## Required Packages

CoreAPIV2 uses `packrat` for package build and runtime dependency management
(See `README.md` for more information).

```{r}
library('knitr')

d<-packageDescription("CoreAPIV2")
imports<-strsplit(d[["Imports"]], "[[:punct:][:space:]]+")[[1]]
importFrame<-data.frame(package = imports)

kable(importFrame, format = "markdown")
```

## Unit Test Results

```{r eval=FALSE}
library('knitr')
library('testthat')

#TODO re-enable block as part of output from running tests in CI 

log<-capture.output(tr<-test_dir("../tests/testthat"))
kable(as.data.frame(tr), longtable = TRUE, font_size = 7)
```
